% start: template for headers and footer info that need to be adde in each pade that includes a section
\chead{\textit{IT-University of Copenhagen} \rangle  SESG-E2013  \rangle \textbf{Group:} 10 Danish Travel card  \rangle \textbf{ID:} 11 \rangle Responsible: All}
\cfoot{\textbf{Hand-in date:} \today \rangle \textbf{Supervisor:} Marco Nardello \rangle \textbf{Version:} 1 \rangle \textbf{Status: } Done \thepage}
\renewcommand{\headrulewidth}{0.1pt}
\renewcommand{\footrulewidth}{0.1pt}
% ends: headers/footers template

\section*{Collaboration Protocol}


\textbf{Purpose:} Shared agreements on overall forms of team collaboration.
\\
\\
\noindent
\textbf{Team members:}
\begin{description}
\item[] Hussein Salem
\item[] Faisal Jarkass
\item[] Aku Nour Shirazi Valta
\item[] Dhiraj Bikram Malla
\item[] Xiaolong Tang
\item[] Jorge Castillo Rodríguez
\end{description}
\\
\\
\noindent
\begin{enumerate}
	\item \textbf{What are the time slots that you can set aside for the team work?}
	Wednesday: after lectures till 14:00 [12:30-14:30]
	At a later point we might change the time
	We could work longer time in the future if we need to.
	
	\item \textbf{ If you disagree with each other or think that the solutions/products of some of the others is not satisfactory, what is the tone of communication?}
	Group discussion / democracy
	
	\item \textbf{What is the maximum length of postings?}
	500 words
	\item \textbf{What do you do if a team member remains silent?}
	One of the team members will talk with that individual. And we might talk about it with the TA
	
	\item \textbf{Do you expect that team members ask for help if they recognize, they do not manage their tasks?}
	Yes. We should have an open dialog where our problems and concern can be discussed
	\item \textbf{Which team conflicts might arise and how do you imagine dealing with them?}
	Deadline issues, help the one that couldn’t do it or perhaps give him more time.
	
	\item \textbf{How and where do you share files?\textit{You might consider google docs, dropbox, or the BSCW.}}
	Google drive - File Sharing
	Google docs - Document editor
	Github - Latex Repository share
	
	\item \textbf{Which tools for communication will you use for what purpose?}
	The main communication tool in our group will be Skype, since it is a free services that provides
live chat, video and file transfer protocol if needed.
	
	\item \textbf{how are you going to communicate asynchronously?}
	We decided to communicate through Skype and emails.
\end{enumerate}