% start: template for headers and footer info that need to be adde in each pade that includes a section
\chead{\textit{IT-University of Copenhagen} \rangle  SSEQ-E2013  \rangle \textbf{Group:} 10 Danish Travel card  \rangle \textbf{ID:} 57 \rangle Responsible: All}
\cfoot{\textbf{Hand-in date:} \today \rangle \textbf{Supervisor:} Marco Nardello \rangle \textbf{Version:} 1 \rangle \textbf{Status: } Done \thepage}
\renewcommand{\headrulewidth}{0.1pt}
\renewcommand{\footrulewidth}{0.1pt}
% ends: headers/footers template

\section*{Explore the user context}
 

\subsection*{Refine your documentation}
\begin{enumerate}
	\item Check in
		\begin{itemize}
			
			\item Machine errors
				\begin{enumerate}
					\item The machine functionality does not work optimal, f.eks. in the bus
				\end{enumerate}
			
			\item Machine is sensitive
				\begin{enumerate}
					\item The machines are too sensitive. People might check in or check out by mistake if they stay close to the check in/ out machines.
				\end{enumerate}
			
			\item Alartive sounds(low balance and check in) are pretty similar
				\begin{enumerate}
					\item Low balance sound and check in sound are similar. Users have no idea they didn’t check in when the card is low balance.
				\end{enumerate}
				
			\item Re-check in
				\begin{enumerate}
					\item People forget to check in when they change transportation under their commute
				\end{enumerate}
		\end{itemize}
	
	\item Check out
		\begin{itemize}
			
			\item Visibility
				\begin{enumerate}
					\item People forget to check out because the machine does not stand out clearly
					\item There is not clear signs that reminds people to check out
				\end{enumerate}
			
			\item Flexibility
				\begin{enumerate}
					\item People who forget to check out, don't have the possibility to check out besides from check out machines
				\end{enumerate}
				
		\end{itemize}
	
	
	\item Service
		\begin{itemize}
		
			\item Children / period card
				\begin{enumerate}
					\item There is no discount for children traveling. They pay the same price as adults
					\item There is no period card service for people who travel a lot
				\end{enumerate}

			\item Flexibility
				\begin{enumerate}
					\item Rejsekort cannot work with other ticket together like period card.
				\end{enumerate}
		\end{itemize}
		
	\item Ideas
		\begin{itemize}
			
			\item Voice sounds
				\begin{enumerate}
					\item Human voice sound in different language accordingly to your choice which can be made online at your account, or at the ticket office. The default language is Danish.
				\end{enumerate}
			
			\item Check in and check out SMS
				\begin{enumerate}
					\item If you did not check out within a certain time, you will receive a sms
				\end{enumerate}
			
			\item Cancel service / Limit service
				\begin{enumerate}
					\item It can change or cancel period service online if rejsekort have more services.
				\end{enumerate}
			
			\item Children service and period service
				\begin{enumerate}
					\item Children service should be half price than adult
					\item Period service allows passengers can check in/ out in the specific zones any time.
					\item Period service can also work with other types of  ticket 
				\end{enumerate}
				
			\item Broadcast / sign
				\begin{enumerate}
					\item remind people to check out and recheck in
					\item Big and clear sign in the stations or buses
					\item QR code on the machine. People can scan it to report it if the machine is broken.
					\item A server listens all the machine status. But it could be very expensive for this.  
				\end{enumerate}
			
			\item Mobile checkout app
				\begin{enumerate}
					\item Check in function only works when you scan QR code on the check in machine. Just in case the machine is broken.
					\item For those who do not have a smartphone, a call system is available
					\item Check out function gets users’ location (zone number) and send back to server to check out.
					\item This app needs mobile phone with GPS and internet access
				\end{enumerate}
			
		\end{itemize}

\end{enumerate}