\section*{Reflection on our Project Team Protocol}

\subsection*{Did you follow the agreement?}
 

Yes, we did follow the agreements.Even though at times changes were needed. We agreed to meet as a group in order to work on the project at Wednesdays after lectures and some weekends as it become more needed for finish all require documents, otherwise we did have enough time to do all work load, in some points during the course there was the need to add more working ours to the project to be able to finish on time and also keep working with the starting idea that all members should be present and participate in all documents creation, but sometimes some members could not meet at some day or hours so Skype meetings were often taken.

%but this quickly changed as we realized it wasn’t enough. We kept meeting on Wednesdays, but had to meet during some of the other days as well. We did see this coming, which is why we in the protocol included that we at times would have to set some more time off. For the most of the time we managed to follow our time slots where all team members were present, but at other times this was harder to realize. In cases where some group members couldn't be present, the rest of gathered, and those who wasn't present could stay tuned via Skype.


Another of the initial agreements was to have some sort of discussion to get the best output for all documents that was the most correct possible and included all team members ideas. Since we are all have different ideas, is a assumption to take that there was some disagreements in some cases, but as a group we found the solution for all this disagreements.
  
%We agreed to have decent group discussions in cases where we disagreed, and our result should be based on democracy. We did face disagreements at times, but as a group we managed to come with a solution and option that we could all agree upon.

There was a very good working environment in the group which made the process more smooth and at the same time made the working time more comfortable and something enjoyable which as the same time help all member to participate since there it was a more friendly working atmosphere. 
%Our group had a good working environment and a smooth process, which made all members comfortable and as a part of the group, and therefore all members contributed to the project and did not keep silent.


Also there it was some agreements in case some team member did not manage to complete some individual task, such adding more time discussing and researching information about the relevant topic to help the team member.
%We agreed to have an open dialog in case any members did manage to make a task that were given them to them. Most of our work were made where all members were present, and we therefore faced and solved most of the problems together. In the cases where a single members faced problems, an open dialog took place where all members added their perspective on the problem and how we could solve it. 

And another very important point in the group was the deadlines, and to find a way to have enough time, therefore as it was mentioned before this was a very important point for us, to find the right time that we all could meet and do all the work together so we all could learn from each others, but sometimes there was not enough time and some work needed to be divided, but the final revision was always conducted with the entire group.
%We expected to face conflict concerning deadlines how we could manage the time. As mention most of the project was done together in the group, and we therefore faced the conflict together. At times where we did not manage live up to the deadlines we had to schedule more time, which we mostly did, but at times this simply wasn't possible which made us divide the work and afterwards reviewed it together.

Most of the work was done via Google Docs, and files sharing using Google Drive, but later the text was formatted to LateX so the sharing was move to Github to be able to have source control. Even though we has some errors in the start while using google drive where most of the files were deleted, but luckily not much was lost.
 
%Most of our sharing were done using Google Drive and later on at GitHub as well. In the early process of our project out Google Drive failed us where we lost most of our work. Luckily we had a back up which were restored. 
%When we were not present and communication was needed it, we used Skype as the main tool and emails if it was more efficient in some cases.
In another cases when communication become harder, because a team member was not present that day at school, family emergency, or any other motive, we try conduct Skype chat or email in case all members were not online at the time of the enquiry.

\subsection*{Did the agreement fulfill the purpose?}

Yes it was, since are started intentions was fulfilled at it maxim that it is possible, all team members become part and contributors of all documents and the creation of each one of them. 
%Our intention related to the time slots we agreed upon, was to make sure all group members could contribute to the project and be a part of the whole process. Our agreement did fulfill the purpose since our intention was met.

Therefore when some team members did face family problems and any other of adverts that could delay them from meeting or just not allow them to participate give time, the rest of the team could take over to help to fulfill all documents and put this fellow member back on track after it was able to join back the team.
%In case any members faced some problem the purpose of the open dialog made sure that the members could feel open to share the problems and not keep them to himself. This was actually a very important agreement, which purpose was met, since in a case where a problem was not shared, it would have affected the whole project in the end.

Even though the scheduling was implement thinking that all members will have to present to develop the documents, some documents deadlines was not possible to meet at time, and this carriage so time pressure by the end. 
%The purpose of scheduling more time in case we did not live up to a certain deadline, was to make sure we would finish the part. The purpose was mostly met, but pushed the deadline of other parts further, which in the end resulted in a certain time pressure.

Thanks to the tools we used for document sharing and communication made sure all group members was updated and could follow the changes that were made.

\subsection*{Would you, with your experience propose a different agreement?}

Seen from an overall perspective we think the agreements were suitable for our group since most purposes were met. It could though in some cases have been efficient if the agreements had been described in more details. This could have given us a deeper clarification when issues arose and easier to find a solution while referring to the agreement. 

What items would you recommend to include in the project team agreement

It would have been useful and very helpful, if we from the beginning had agreed on how the work structure should take place. An agreed work structure could have made us more efficient concerning our time management.

Agreeing upon which text editor we would use could likewise have been efficient, since we needed to convert documents back and forth. This could at times be very confusing and hard to keep track on the document version.

Seen from an overall perspective we satisfied with the outcome of the project, even though it was a learn full challenge. We managed to look into all the assignments and its related theory. The course, the related project and the process we undertook have been interesting and useful, especially when seen from a professional perspective related to the activities in software engineering. The course addressed a wide range of aspects which gave us a insight and understanding of the processes of software development takes place. Working with the Danish Rejse kort system reinforced or insight and understand, since it was something we could relate to in our daily life.

If we look in to each separate case, we think there a still areas which can be improved. When we reached a certain points in our project, we reflected on some of the work we had done earlier on, and could easily that we could made it a different way or improved it. We did manage to improve some of the work based on the reflection and also based on the reviews, but there is to a degree still room for improvements.