% start: template for headers and footer info that need to be adde in each pade that includes a section
\chead{\textit{IT-University of Copenhagen} \rangle  SSEQ-E2013  \rangle \textbf{Group:} 10 Danish Travel card  \rangle \textbf{ID:} 61 \rangle Responsible: All}
\cfoot{\textbf{Hand-in date:} \today \rangle \textbf{Supervisor:} Marco Nardello \rangle \textbf{Version:} 1 \rangle \textbf{Status: } Done \thepage}
\renewcommand{\headrulewidth}{0.1pt}
\renewcommand{\footrulewidth}{0.1pt}
% ends: headers/footers template

\section*{Use Case Description}

\subsection*{Actors}

\textbf{Customer:}
A person who uses the Rejsekort system or buys it on behalf of another person.

\textbf{Customer service:}
A person who works for the Rejsekort company serving the customers. A person in the customer service can do the same as the customer except for checking in and checking status.

\textbf{Controller:}
A person who checks whether passengers with Rejsekort are commuting a valid trip. In case they are not, the controller is able to issue them a fine.

\textbf{Financial institute:}
Withdraws money from the customers account whenever they checkout or add credit to their balance, either by them self or through the customer service.

\subsection*{Use cases}
\textbf{BlockAccount:}
An account can be blocked either by the customer or the customer service.

\textbf{CheckBalance:}
The balance of a customer can be checked both by the customer and the customer service.

\textbf{BlockCardAccount:}
A customer or the customer service can block a specific card on a customer account.

\textbf{CreateAccount:}
A customer can create an account or request the customer service to create it.

\textbf{AddBalance extends Withdraw :}
The customer service or the customer can add balance to his account.

\textbf{CheckOut extends Withdraw:}
When a passenger ends his commute he is able to checkout, which also can be done by the customer service in cases it is needed

\textbf{Withdraw:}
Depending on the customers choice, the financial institute withdraws money from the customers bank account when balance is added to the Rejsekort account or when checking out.

\textbf{CheckHistory:}
The customer service or the customer himself can check the history of activities on the account.

\textbf{CheckCustomerStatus:}
Its possible for the customer, the customer service and the controller to check whether the passenger traveling on Rejsekort have checked in.

\textbf{SendMail:}
Both the customer and service can communicate by mail.

\textbf{EraseFine:}
The customer service can erase a fine given to a customer.

\textbf{CheckIn:}
A passenger traveling with Rejsekort can check-in when he starts his commute and if he wish he can add:
\begin{enumerate}
	\item AddBicycle
	\item AddAnimal
	\item AddAdults
	\item AddKids
\end{enumerate}

\textbf{GiveFine:}
The controller can give a passenger a fine.