\section*{Interviews Summary}

\subsection*{Interview to ticket controller}
\textit{26. sep. 2013 15:05} at DR Byen station

\textbf{Have the Rejsekort system made your work easier?}
\textit{“In the start there were many problems, but it have become better over time, which makes by work a bit easier”}

\textbf{Which problems do you see the passengers face?}
\textit{“The passengers using travel card(Rejsekort) forget to check in again when they change transport means under their commute. This entitles them to a fine, which we (controllers in the metro) have stopped to hand out, as there have been much confusion since the travel card came”}



\subsection*{Interview to IT professionals}
\textbf{Observation}
\textit{26/9-2013 15:00-15:20} at DR Byen station
A guy is coming up to the station. He uses his clips card and walk away. A metro just comes in to the station. Around 8 passengers come out. And 2 people get into the train. A little girl comes and check out with a Rejsekort. Then a guy is coming up to the station. He uses his clipe card and wait for the metro. Two guys are coming to station and use their clipe card. After that they are waiting for the train.Then a man put his wallet close to check in machine. Then a man and a woman are coming up to DR station. The man check in with his clipe card. the woman put her wallet close to the check in machine. 
A guy comes up with his Rejsekort. He checks in and wait for the metro. Then a train is coming into station. A woman is very hurry up to use her clipe card. But her card is bended. So she tries many times and finally she check in with her clipe card. But she missed the trains.
\\
\\
Another train is coming in to station. Many passengers are coming out. Passengers who use rejsekort are standing around the check out machine. Because they are waiting for the passengers who are in front them to check out. Two little girls, they are coming up to the station. They both check in with rejsekort. And they are waiting in the train station.
A guy is checking out, but have problems seeing the display on the machine because the sun is reflecting on it. Another woman is checking several people in, but seems a bit confused.
\\
\\
\textit{27/9-2013 8:30-8:45} DR Byen station
A guy who take a cup of coffee is coming up to the train station.He puts his rejsekort from his pocket. And he puts close to check in machine. The trains are coming every 4 minutes. There are a lot of people are waiting in the train station. There are crowd of people are standing in front of check out machines. Then a train is coming to station. there are around 12 people getting off from that train. A girl takes rejsekort. She press the machine. She checks in not only for her but also for her friend. There are still a crowd of people in the station. There are 3 people standing in front of check out machine.
\\
\\
A train is coming in to station. Most of people go inside. And two little girls are coming out of train. Two men are coming up to station. They both check in with rejsekort.

