\section*{Interview Questions}

\textbf{There will be 3 participants} 
\begin{enumerate} % start:1
	\item passagers(structured)
		\begin{enumerate} % start :2
			\item Rejse Kort users
				\begin{enumerate}
					\item How old are you? 
					\begin{enumerate}Range:
						\item 15 - 25
						\item 26- 35
						\item older
				\end{enumerate}
				
			\item How often do you use Rejse Kort?
				\begin{enumerate}
					\item Every day
					\item 1-3 times a week
					\item 1-3 times a month
					\item twice a year
					\item or less
				\end{enumerate}
				
			\item Which type of Rejse kort are you using?
				\begin{enumerate}
					\item Personal card (Rejsekort personligt)
					\item Anonymous card (Rejsekort anonymt)
					\item Flex card (Rejsekort flex)
				\end{enumerate}
				
			\item How did you order your Rejse Kort?
				\begin{enumerate}
					\item Online
					\item Ticket office
				\end{enumerate}
				
			\item How do you charge your Rejse Kort?
				\begin{enumerate}
					\item Dankort agreement / automatic recharge
					\item Online
					\item Machine
					\item Ticket office
				\end{enumerate}
				
			\item Which transportation do you use very often?
				\begin{enumerate}
					\item Metro
					\item regular train
					\item S train
					\item bus
					\item boat
				\end{enumerate}
				
			\item Why do you choose Rejse kort at the beginning?
				\begin{enumerate}
					\item price
					\item new technology
					\item convenient(easy, cover all Denmark etc.)
					\item others...
				\end{enumerate}
				
			\item What the problems are you facing when you use Rejse Kort?
				\begin{enumerate}
					\item Checking in
					\item Checking out
					\item Loading credit/balance
					\item No, I don’t have yet
					\item If yes, Please explain
					\item Other problems?
				\end{enumerate}
				
			\item Which improvement  do you expect from Rejse Kort?
				\begin{enumerate}
					\item Open answer
				\end{enumerate}	
		\end{enumerate}% ends :2
		
	\item non user passengers
		\begin{enumerate} %start: inner 1
			\item How old are you?
				\begin{enumerate}Range
					\item 15 - 25
					\item 26- 35
					\item older
				\end{enumerate}
			
			\item How often do you use public transportation?
				\begin{enumerate}
					\item Every day
					\item 1-3 times a week
					\item 1-3 times a month
					\item twice a year
					\item or less
				\end{enumerate}
			
			\item Which type of tickets are you using?
				\begin{enumerate}
					\item single ticket
					\item period card
					\item youth card
					\item clip card
					\item app ticket
					\item pension card
					\item other
				\end{enumerate}
			
			\item Why are you not using Rejse Kort?
				\begin{enumerate}
					\item Price
					\item New technology
					\item Difficult
					\item Not convenient
					\item other
				\end{enumerate}
			
			\item Which improvement would you suggest Rejser Kort then you can use it in the future?
				\begin{enumerate}
					\item Open answer
					\item I would never use it
				\end{enumerate}	
		\end{enumerate}%ends: inner 1		
	%\end{enumerate}
	
	\item company IT professionals(semi-structured)
		\begin{enumerate}
			\item How do you think about rejse kort system?
			\item Which kind of problems do you face with the Rejse Kort system ?
			\item What could be improved? and how?
			\item How many percent of users in Denmark do your company expectful? 
		\end{enumerate}
		
		\item ticket controllers(semi-structured)
			\begin{enumerate}
				\item Which kind of problems do you face working with the Rejse Kort system ?
				\item What could be improved?
				\item How does this card help you work? F.x make easy for your work?
				\item Which of the transportation ticket you prefer? why?
		\end{enumerate}

\end{enumerate}  % ends:1


It can be concluded from our observation and interview that the current Danish TravelCard system have issues which can be improved and corrected. Some of the problem are listed below:

\begin{itemize}%[leftmargin=1em]
  \renewcommand{\labelitemi}{$\Rightarrow$}
 	\item Passengers did not manage to find out how to check out, or simply forgot to do so.
 	\item The fair billed was not the cheapest fare as promised in the advertisement, especially for kids and pensioners.
	\item Passengers who were accused by ticket controllers of not paying could not proof that they had checked in though they, at least, thought they did so. Passengers do not get a receipt. With other words: errors caused by the system could not be proven to the ticket controller.
	\item Control over billing data and privacy – also in the light of the current revelation of privacy issues with foreign and local authorities collecting data ‘for stock’ is an issue as well.
	\item The sounds is coming from the machine is quite confusing to the passengers.
	\item The machine is sometimes not functioning thus making it hard to check in or check out.
	\item The out and check in machines look very similar.
\end{itemize}
